Accurate binding of calcium to phospholipid bilayers by effective inclusion of electronic polarization

### 2017-10-05 Manuscript/manuscript.tex
Moved delta-OP plots into SI.

\begin{figure}[tbp]
  \centering
  \includegraphics[width=8.0cm]{../Fig/ipython_nb/PN_angle_OrdPars-A-B_L14-ECCL17_q80_sig89_NaCl.pdf}
  \caption{\label{fig:delta_ordPar_NaCl}
    Changes of head group order parameters of POPC bilayer as a function of NaCl concentrations
    are shown from simulations with different force fields together with experimental data \cite{akutsu81}. 
    Ion concentrations in bulk water are shown in x-axis. 
    Values from simulations are calculated from the of cation number density $C_{np}$
    from the region at the simulatin box edge with the constant ion concentration as [ion]=$C_{np}/0.602$.
    Simulation data with Lipid14 and \AA{}qvist ion parameters is taken directly from Ref. \cite{catte16}.
  }
\end{figure}
\begin{figure}[tbp]
  \centering
  \includegraphics[width=7.5cm]{../Fig/ipython_nb/PN_angle_OrdPars-A-B-g3_L14-ECCL17_q80_sig89_CaCl.pdf}
  \caption{\label{fig:delta_ordPar_CaCl}
    Changes of head group order parameters of POPC bilayer as a function of CaCl$_2$ concentrations
    are shown from simulations with different force fields together with experimental data 
    (DPPC \cite{akutsu81} and POPC \cite{altenbach84}). 
    Ion concentrations in bulk water are shown in x-axis. 
    Values from simulations are calculated from the of cation number density $C_{np}$
    from the region at the simulatin box edge with the constant ion concentration as [ion]=$C_{np}/0.602$.
    Simulation data with Lipid14 and \AA{}qvist ion parameters is taken directly from Ref. \cite{catte16}.
  }
\end{figure}

The binding affinity of aqueous cations in lipid 
bilayers can be measured by using the headgroup 
order parameters, because they decrease proportionally  
to the bound positive charge~\cite{seelig87,catte16}. 
The headgroup order parameter responses 
to aqueous NaCl and CaCl$_2$ concentrations 
are shown in Fig. \ref{fig:delta_ordPar_NaCl} and \ref{fig:delta_ordPar_CaCl}
from experiments (DPPC \cite{akutsu81} 
and POPC \cite{altenbach84}) and different simulation models for POPC.

@@

Significant improvement can be achieved by using the ECC
approach also for lipids. The headgroup order parameter changes
as a function of CaCl$_2$ concentration from ECC-lipid model with ECC-ions
show a good agreement with experiments in Fig. \ref{fig:delta_ordPar_NaCl} and \ref{fig:delta_ordPar_CaCl}.
As discussed in previous section, the model gives also
a good agreement with experiments for
the headgroup response to bound charge.
Thus, the model can used for more detailed analysis of the
binding affinity.

@@

>>>>

\begin{figure}[tbp]
  \centering
  \includegraphics[width=7.5cm]{../Fig/ipython_nb/PN_angle_OrdPars-A-B-g3_L14-ECCL17_q80_sig89_CaCl.pdf}
  \caption{\label{fig:delta_ordPar_CaCl}
    Changes of head group order parameters of POPC bilayer as a function of CaCl$_2$ concentrations
    are shown from simulations with different force fields together with experimental data 
    (DPPC \cite{akutsu81} and POPC \cite{altenbach84}). 
    Ion concentrations in bulk water are shown in x-axis. 
    Values from simulations are calculated from the of cation number density $C_{np}$
    from the region at the simulatin box edge with the constant ion concentration as [ion]=$C_{np}/0.602$.
    Simulation data with Lipid14 and \AA{}qvist ion parameters is taken directly from Ref. \cite{catte16}.
  }
\end{figure}

The binding affinity of aqueous cations in lipid 
bilayers can be measured by using the headgroup 
order parameters, because they decrease proportionally  
to the bound positive charge~\cite{seelig87,catte16}. 
The headgroup order parameter responses 
to aqueous NaCl and CaCl$_2$ concentrations 
are shown in Fig.~\ref{fig:delta_ordPar_CaCl} and S\ref{fig:delta_ordPar_NaCl}
from experiments (DPPC \cite{akutsu81} 
and POPC \cite{altenbach84}) and different simulation models for POPC.

@@

Significant improvement can be achieved by using the ECC
approach also for lipids. The headgroup order parameter changes
as a function of CaCl$_2$ concentration from ECC-lipid model with ECC-ions
show a good agreement with experiments in Fig.~\ref{fig:delta_ordPar_CaCl} and S\ref{fig:delta_ordPar_NaCl}.
As discussed in previous section, the model gives also
a good agreement with experiments for
the headgroup response to bound charge.
Thus, the model can used for more detailed analysis of the
binding affinity.

@@

\begin{figure}[tbp]
  \centering
  \includegraphics[width=8.0cm]{../Fig/ipython_nb/PN_angle_OrdPars-A-B-g3_L14-ECCL17_q80_sig89_NaCl.pdf}
  \caption{\label{fig:delta_ordPar_NaCl}
    Changes of head group order parameters of POPC bilayer as a function of NaCl concentrations
    are shown from simulations with different force fields together with experimental data \cite{akutsu81}. 
    Ion concentrations in bulk water are shown in x-axis. 
    Values from simulations are calculated from the of cation number density $C_{np}$
    from the region at the simulatin box edge with the constant ion concentration as [ion]=$C_{np}/0.602$.
    Simulation data with Lipid14 and \AA{}qvist ion parameters is taken directly from Ref. \cite{catte16}.
  }
\end{figure}
